Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-23 parts/morph.tex
some changes
fix image cutout zoom

\section{Image morphology}\label{sec:morph}

@@

We now discuss the diagnostics that can be taken from the process of
drawing the spaghetti diagram, even before detailed mass-modelling
takes place.  Figure~\ref{fig:splinput} shows nine examples, each
consisting of a cutout of the Space~Warps image of a lens candidate,
marked up with a spaghetti diagram.

>>>>

\section{Image morphology}
\label{sec:morph}

@@

We now discuss the diagnostics that can be taken from the process of
drawing the spaghetti diagram, even before detailed mass-modelling
takes place.  Figure~\ref{fig:splinput} shows nine examples, each
consisting of a cutout of the Space~Warps image of a lens candidate,
marked up with a spaghetti diagram.
The volunteers are initially presented the original Space~Warps image of
length and height 82\arcsec (440~pixels) in full size, but they have the
ability to zoom in individually.
The cutouts presented in Figures~\ref{fig:splinput} to \ref{fig:encl}
are rescaled in post processing relative to the outermost image identified.
% it's a factor L/(L-4) with L=pixradius, for L=12 -> 1.5
% maprad = rmax * L / (L-4)
